\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{hyperref}
\hypersetup{breaklinks=true}
\usepackage{longtable,booktabs}
\usepackage{fullpage}

\title{ADCL Student-Advisor Agreement}
\author{Professor Zachary Sunberg}
\date{Last revised: \today}

\begin{document}

\maketitle

\section{Purpose}

Your PhD in the ADCL will be many things: hard. The purpose of this document is to establish expectations for how we will interact . It is not a formal contract, but merely a set of guidelines so that you can know what to expect

\textbf{{Purpose:\\
}}\emph{Example:}

\textbf{{Lab Hours are:}}

\emph{Example: Generally, 7 AM to 4 PM for me, and ideally our paths
would cross during that time. If you're not a `morning person' I'd
expect you to work later in the day. I expect you to come to lab
meetings which are on X days at X time. You're an adult, so I expect you
to manage that time yourself, and I expect the work will get done. How
you want to schedule that time is up to you.}

\textbf{{If you want to reach me:}\\
}\emph{Example: Email is always good, in person is great but I'm not
always in the immediate vicinity. Feel free to drop in when we're not
having our one on one. When my door is closed please do not disturb. My
cell is X and my office is room Y.}

\textbf{{When I go out of town:\\
}}\emph{Example: I will let you know. If it's a personal vacation, I'll
be offline. If it's professional (conference, talk, etc) I'll still be
reachable but my emails will be delayed. I keep a calendar at X so
you'll know where I am and when I'll be back. If there's an issue that
needs immediate assistance, please speak to \textless{}Lab
Manager\textgreater{} until I am back.}

\textbf{{If I email you:}\\
}\emph{Example: I expect a response within 2 business days, if I would
like a faster response (during tight deadline times) we will have a
conversation about that. Generally, if I email on weekends I don't
expect an answer until Monday during lab hours, unless we're up against
a deadline and we've had a discussion about emailing outside of the
workweek. I do not expect late night responses or very early morning
responses if I email during those times. I do, however, expect a
response.}

\textbf{{If you email me:}\\
} \emph{Example: I will respond to all emails from you within 2-3
business days. If I am on travel, this can be delayed. I'll be sure
you're aware of when I will be offline. If I don't respond during
`normal times', please email again -- I get a great deal of email so
sometimes I need to be reminded.}

\textbf{{If you want to go on a vacation:}}

\emph{Example: Just give me 3 weeks' notice. Certain times of year are
bad for travel. Such as during the school year when you are TA'ing.
We'll coordinate a calendar to make sure the needs of the lab are
covered. For family emergencies, obviously no notice is needed (but
please let me know you are out so I don't worry). Students in my lab get
2 weeks vacation a year, plus major university holidays.}

\textbf{{If you are sick:}\\
}\emph{Example: Please do not come to the lab. Rest and get well, see a
doctor if you need to. If you need to communicate anything serious,
please let me know (I don't need details, but I do want to know how you
are doing).}

\textbf{{If you make a mistake:}\\
}\emph{Example: Please come to me or to a postdoc in the lab. Mistakes
happen during grad school, and during the scientific process. THIS IS
NORMAL. This is how we learn.}\textbf{\\
{~\\
If you and I are in conflict:}}{\\
}\emph{Example: We should try to resolve the problem informally first,
but if you don't feel like I'm hearing your concern or you feel
uncomfortable raising it with me, you should first go to the graduate
advisor (if you don't need confidentiality) or the Ombuds office (if you
need confidentiality). They should help you with mediation, and will
direct you to formal complaint avenues should it prove necessary.}

\textbf{{If you feel your research interests have changed OR our working
relationship is not the best fit:}}

\emph{Example: It is okay to let me know if your research interests have
changed, OR if you feel the working culture in this lab is not the best
fit for you. Please feel free to come and discuss with me on this. We
can sort out issues together and work on your next plan of action or
next steps to succeed in the PhD program.}

\textbf{{Core values of my lab (List 5):}\\
}\emph{Example: Respect. Accountability. Perseverance. Compassion.
Support.}

\textbf{{Lab Culture:}\\
}\emph{Example: I work hard to maintain a respectful lab culture. If at
any time there is an issue between lab mates I hope it can be resolved
through discussion and mutual respect. If it becomes a problem, please
bring it to me. Everyone should feel safe, supported, and empowered.}

\textbf{{Graduate School is:}\\
}\emph{Example: Not easy! It's a marathon, and there will be ups and
downs throughout the process. You may feel like a failure, or an
imposter. THIS IS NORMAL. Please know you were brought into my lab for a
good reason, and I am here to support you -- work hard and don't give
up. You can do this!}

\textbf{{EXPECTATIONS FOR GRADUATE STUDENTS:}}

\textbf{{Department Expectations:}}

See the graduate handbook \textless{}link\textgreater{}

\textbf{{Expectations Specific to My Lab:}}

\textbf{{\textless{}Make use of a table to provide lab-specific
milestones; Customize as needed\textgreater{}}}

\begin{longtable}[]{@{}llllllll@{}}
\toprule
\textbf{Lab milestones} & \textbf{Year 1} & \textbf{Year 2} &
\textbf{Year 3} & \textbf{Year 4} & \textbf{Year 5} & \textbf{Year 6} &
\textbf{Notes}\tabularnewline
\midrule
\endhead
~ & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Master equipment & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Read X papers & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Publish a paper & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Go to a conference & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Give annual talk & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Present at lab meeting & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
~ & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
Broad goals: & ~ & ~ & ~ & ~ & ~ & ~ & ~\tabularnewline
\bottomrule
\end{longtable}

\textbf{{\textless{}List other lab-related expectations
here\textgreater{}}}

\textbf{{What I expect from YOU:\\
}}

\textbf{When you graduate from my lab I hope you:}

\textbf{I expect you to manage your pace to and goals of the PhD by:\\
}

\textbf{I expect you to communicate to others in my lab:}

\textbf{I hope you obtain research skills and abilities in:}

\textbf{I expect your communication with me (and others):}

\textbf{My expectations for deadlines are:}

\textbf{{What You Should Expect From Me:}}

\textbf{As a mentor I promise to:}

\textbf{In regard to your career goals I promise to:}

\textbf{Feedback from me will be:}

\textbf{You will be evaluated on your progress (on project and towards
degree -- how often?):}

\textbf{This document serves both the advisee and the advisor by
providing agreed-upon guidelines which will clarify expectations, lessen
conflict and provide structure. }

\emph{The information contained in this document is intended to provide
recommended best practices and guidelines for graduate student
mentoring. It is not intended to, nor does it, create an express or
implied contract between the advisor and advisee or between or among the
university and any faculty member or graduate student. }

\textbf{Please feel free to add any other points of concern below prior
to initialing.}


\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

Student Initials: Advisor Initials:


\end{document}
